Abstractions for Multi-Sorted Substitutions

### 2023-08-30 paper/paper.tex
Update.

  But to unify those two compositions, we need a new abstraction:
  \ExampleCode\KComposition
  The Kit-abstraction from before allowed us to abstract over what we
  apply, i.e.\ a renaming or a substitution, but not about what we apply it
  to, i.e.\ a variable or a term. For the latter we still have two
  distinct operations \ACode{\ADef{\_\&\_}} and \ACode{\ADef{\_⋯\_}}.
  A \ACode{\ACon{ComposeKit} K₁ K₂ K₁⊔K₂} fills exactly that gap by providing
  the operation \ACode{\ADef{\_\&/⋯\_}} which applies a renaming/substitution (\ACode{K₂})
  to a variable/term (\ACode{K₁}) and produces a variable/term (\ACode{K₁⊔K₂}).

>>>>

  But to unify those two compositions, we need a new abstraction:
  \ExampleCode\KComposition
  The Kit-abstraction from before allowed us to abstract over what we
  apply, i.e.\ a renaming or a substitution, but not about what we apply it
  to, i.e.\ a variable or a term. For the latter we still have two
  distinct operations \ACode{\ADef{\_\&\_}} and \ACode{\ADef{\_⋯\_}}.
  A \ACode{\ACon{ComposeKit} K₁ K₂ K₁⊔K₂} fills exactly that gap by providing
  the operation \ACode{\AField{\_\&/⋯\_}} which applies a renaming/substitution (\ACode{K₂})
  to a variable/term (\ACode{K₁}) and produces a variable/term (\ACode{K₁⊔K₂}).
  We want to have a ComposeKit for each \ACode{K₁} and \ACode{K₂},
  where the output Kit \ACode{K₁⊔K₂}, is defined as a function of
  \ACode{K₁} and \ACode{K₂}, similar to functional dependencies in Haskell.
  If \ACode{K₁} and \ACode{K₂} are both the variable kit \ACode{Kᵣ},
  then \ACode{K₁⊔K₂} is also the variable kit \ACode{Kᵣ}. But if either
  \ACode{K₁} or \ACode{K₂} is a term kit \ACode{Kₛ}, then also
  \ACode{K₁⊔K₂} is the term kit \ACode{Kₛ}. This is captured in the
  notation \ACode{K₁⊔K₂}, referring to the partial order generated by
  \ACode{Kᵣ < Kₛ}.

  \ACode{\ACon{ComposeKit}} and \ACode{\ACon{\_\&/⋯\_}} are analogous to
  \ACode{\ACon{Kit}} and \ACode{\ADef{\_→ₖ\_}}, whereas
  \ACode{\ACon{ComposeTraversal}} and \ACode{\AField{⋯-assoc}} are analogous to
  \ACode{\ACon{ComposeTraversal}} and \ACode{\AField{\_⋯\_}}.
